A Systematic Review of the Use of the ESM Methodology in Education

### 2020-08-26 paper_draft.Rmd
save changes
Clean up
Getting decriptions setup and beginning the wiriting for each section

This study  is a systematic review of studies in education that used the experience sampling method to collect data.

@@

>>>>

This study is a systematic review of studies that used the experience sampling method to collect data in education settings.

@@

# Discription of areas of interest (coding)
 **will work on further description and detail**

## Construct

## Content Area

## Age/Grade Level

## Role of participant

## Sample Size

## Prompting Method

## Number of Signals

## Length of Signaling Period (study length)

## Response Rate

## Signal Method

## Items used

## Discription of items

## Number of Items

## Validity and Reliability

## Missing Data Strategies

## Types of Analysis
